Income Has Serious Implications On Many Facets of American Life in 2021

### 2022-03-20 outputs/paper/paper.Rmd
second commit

---
title: "My titleXXXXXXXXXXXXXXXX"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
```

@@

Our data is of penguins (Figure \@ref(fig:bills)).

```{r bills, fig.cap="Bills of penguins", echo = FALSE}
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = FALSE) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

Also bills and their average (Figure \@ref(fig:billssssss)). (Notice how you can change the height and width so they don't take the whole page?)

```{r billssssss, fig.cap="More bills of penguins", echo = FALSE, fig.width=8, fig.height=4}

# This needs to be about the random data tha tI sasmpled?
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = FALSE) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

>>>>

---
title: "Income Has Serious Implications On Many Facets of American Life in 2021"
subtitle: "A Look Into The Implications of Americans' Incomes Reveals Information On Disparity of The Gender Pay and the American Dream."
author: 
  - Adam Labas  
  - Krupali Bhavsar
thanks: "Code and data are available at: XXXXXXXXXXXXXXXXXXXXXXX"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r setup, fig.pos = "!H", include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(janitor)
library(dplyr)
library(tidyr)
library(opendatatoronto)
library(knitr)
library(patchwork)
library(lubridate)
```

@@

In this Data Section \@ref(data), we will provide a look into the data acquisition and processing methodology as well as a deep dive into the contents of the data. First of, (Table \@ref(tab:tableofdata)) give us a glimpse of the data.

## Data Collection

All of the data used in this analysis was directly collected from the United States 2021 General Social Survey, available here: https://gss.norc.org/ (link and additional information available in the README.md file.) We downloaded the desired data in the STATA format. The zip file acquired included 4 files: a read me text file, the raw data as a dta file, as well as two pdf files. *GSS 2021 Codebook R1b* is essentially the instruction manual for the data set. It does over
